HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
edits

@@

Another problem with HMEANT identified by \parcite{bojar:wu:ssst:2012} was the

inability to indicate that the predicate is somewhat mistranslated (e.g.
accidentally negated or in a slightly wrong tense). HMEANT
annotation allows either to mark the source and reference frames as matching
(which implies that the corresponding predicates are correct translations of each
other), or as non-matching (which leads to a zero score for the whole frame) but
nothing in between. In HUME, the verb is still present as a sub-unit of the
frame and has the traffic-lights annotation.

\oa{I would consider adding further examples from the Google Doc. For instnace ``your risk of falling'' -- ``Ihr Risiko'' or
  ``Two {\bf review} authors assessed the studies independently and extracted outcome data'' -- ``Zwei Autoren bewertete die Studien unabh\"angig zu {\bf \"uberpr\"ufen}''}

>>>>

It is also relatively common in translation that verbal constructions get
nominalized or vice versa. An example from our dataset:
  ``Two {\bf review} authors assessed the studies independently\dots{}'' --
  ``Zwei Autoren bewertete die Studien unabh\"angig zu {\bf
  \"uberpr\"ufen}\dots{}'' (lit. ``Two authors assessed the studies
  independently to be reviewed\dots").\XXX{This is Omri's example, with
  Ondrej's gloss for German. Ondrej is
  not totally sure that the meaning is well preserved.}

@@

Another problem with HMEANT identified by \parcite{bojar:wu:ssst:2012} was the
inability to indicate that the predicate is somewhat mistranslated (e.g.
accidentally negated or in a slightly wrong tense). HMEANT
annotation allows either to mark the source and reference frames as matching
(which implies that the corresponding predicates are correct translations of each
other), or as non-matching (which leads to a zero score for the whole frame) but
nothing in between. In HUME, the verb is still present as a sub-unit of the
frame and has the traffic-lights annotation.

\XXX{Omri: I would consider adding further examples from the Google Doc. For instnace
``your risk of falling'' -- ``Ihr Risiko''.
Ondrej: I don't see any HMEANT problem here, the whole NP 'your risk of falling'
is aligned with 'Ihr Risiko' and HMEANT allows to indicate that the match was
partial, to that's probably what everyone would choose. I've put the other
example higher, but please have a look, I'm not sure if we should keep it there
at all.}
